Expert-In-The-Loop Causal Discovery: \\ Iterative Model Refinement Using Expert Knowledge

### 2025-06-10 paper/main.tex
definitions and pseudocode

\Fn{{\sc ExpertInLoop}($V,\mathcal{D}_G,\mathcal{A}_G$)}{
$E_p \gets \emptyset$ \tcc{Current edges} 
$B \gets \emptyset$ \tcc{Edges that were pruned} 
\Repeat{ $E=E_p$ }{
	$E \gets E_p$ \;
	$(V,E) \gets \textsc{Expand}(V,E,\mathcal{D}_G,\mathcal{A}_G,B,1)$ \;
	$(V,E_p) \gets \textsc{Prune}(V,E,\mathcal{D}_G)$ \;
	$B \gets B \cup \{ E_p \setminus E \} $
}
\Return{(V,E)}
}

>>>>

\Fn{{\sc ExpertInLoop}($V,\mathcal{D}_G,\mathcal{A}_G$)}{
$E_p \gets \emptyset$ \tcc{Current edges} 
$B \gets \emptyset$ \tcc{Edges that were pruned or removed from cycles} 
\Repeat{ $E=E_p$ }{
	$E \gets E_p$ \;
	$(V,E,B<D-s>) \gets \textsc{Expand}(V,E,\mathcal{D}_G,\mathcal{A}_G,B,1)$ \;
	$(V,E_p) \gets \textsc{Prune}(V,E,\mathcal{D}_G)$ \;
	$B \gets B \cup \{ E_p \setminus E \} $
}
\Return{(V,E)}
}
